Predicting Sequence Variability from Voronoi Tessellation of Proteins

### 2015-03-23 manuscript/voronoi/mnv.tex
minor corrections to MN

    A variety of site-specific structural characteristics have been proposed over the past decade to predict protein sequence evolution from structural properties. Among the most important and widely discussed are the Relative Solvent Accessibility (RSA) \citep[e.g.,][]{goldman_assessing_1998, bustamante_solvent_2000, conant_solvent_2009, franzosa_structural_2009, ramsey_relationship_2011, scherrer_modeling_2012, meyer_integrating_2013, meyer_cross-species_2013, yeh_local_2014, yeh_site-specific_2014, shahmoradi_predicting_2014, sikosek_biophysics_2014}, Contact Number \citep[e.g.,][]{rodionov_sequence_1998, hamelryck_amino_2005, liao_protein_2005, bloom_structural_2006, huang_mechanistic_2014, marcos_too_2014, yeh_site-specific_2014, yeh_local_2014, shahmoradi_predicting_2014}, measures of thermodynamic stability changes due to mutations at individual sites in proteins \citep[e.g.,][]{wilke_predicting_2005, echave_relationship_2014}, and measures of local flexibility, such as the Debye-Waller factor (hereafter B factor) \citep[e.g.,][]{liao_protein_2005, shih_evolutionary_2012, shahmoradi_predicting_2014} or flexibility measures based elastic network models \citep[e.g.,][]{liu_sequence_2012} and Molecular Dynamics (MD) simulations \citep[e.g.,][]{shahmoradi_predicting_2014}. \\

>>>>

    A variety of site-specific structural characteristics have been proposed over the past decade to predict protein sequence evolution from structural properties. Among the most important and widely discussed are the Relative Solvent Accessibility (RSA) \citep[e.g.,][]{goldman_assessing_1998, bustamante_solvent_2000, conant_solvent_2009, franzosa_structural_2009, ramsey_relationship_2011, scherrer_modeling_2012, meyer_integrating_2013, meyer_cross-species_2013, yeh_local_2014, yeh_site-specific_2014, shahmoradi_predicting_2014, sikosek_biophysics_2014, meyer_geometric_2015}, Contact Number \citep[e.g.,][]{rodionov_sequence_1998, hamelryck_amino_2005, liao_protein_2005, bloom_structural_2006, huang_mechanistic_2014, marcos_too_2014, yeh_site-specific_2014, yeh_local_2014, shahmoradi_predicting_2014, meyer_geometric_2015}, measures of thermodynamic stability changes due to mutations at individual sites in proteins \citep[e.g.,][]{wilke_predicting_2005, echave_relationship_2014}, and measures of local flexibility, such as the Debye-Waller factor (hereafter B factor) \citep[e.g.,][]{liao_protein_2005, shih_evolutionary_2012, shahmoradi_predicting_2014} or flexibility measures based elastic network models \citep[e.g.,][]{liu_sequence_2012} and Molecular Dynamics (MD) simulations \citep[e.g.,][]{shahmoradi_predicting_2014}. \\
